---
title: "Data_analysis for meta analysis of self-reported and logged media use"
author: "Douglas A. Parry"
date: "September 2020"
output: html_document
---
############## Section 0: READ ME ############## 

This is the analysis code for a meta-analysis on the associations between self-reported and logged measures of digital media use.

The code was written in R version 4.0.2 using RMarkdown (available at: http://rmarkdown.rstudio.com/). It is recommended that this file be downloaded and viewed in RStudio to view the output of the code.

Note on expected directory structure.

- This analysis file (data_analysis.Rmd) expects the file Data_Extraction.xlsx to be in the same directory. All other directories and files are created by the script itself.

############## Section 1: Setup ############## 

# Load packages, clear environment, set seed, and turn scientific notation off
```{r setup, message=FALSE, warning=FALSE}
rm(list = ls())
options(scipen = 999)
set.seed(42)

if (!require("pacman")) install.packages("pacman"); 
library(pacman)
pacman::p_load(tidyverse, dplyr, metafor, MAc, clubSandwich, readxl, TOSTER, robumeta, psych)

#Create expected directory structure:

wd <- getwd()
if (!dir.exists("clean_data")) {dir.create(file.path(wd, "clean_data"))}
if (!dir.exists("figures")) {dir.create(file.path(wd, "figures"))}
```

# Information on the packages used for the analysis
```{r getSessionInfo}
sessionInfo()
```

############## Section 2: Data Processing ############## 

# Import and transform raw data 
```{r}
raw_data <-read_excel("Data_Extraction.xlsx", na="NA")

raw_data <- raw_data %>% mutate(effect_ID = paste0(Study_ID, Comparison_ID))

raw_data$sr_outcome_type <- factor(raw_data$sr_outcome_type)
raw_data$medium <- factor(raw_data$medium)
raw_data$use_measurement <- factor(raw_data$Use_Measurement_Produced)
raw_data$Population_Type <- factor(raw_data$Population_Type)
raw_data$Sampling_Category <- factor(raw_data$Sampling_Category)
raw_data$Log_Collection_category <- factor(raw_data$Log_Collection_category)
raw_data$Log_Source <- factor(raw_data$Log_Source)
raw_data$SR_Form <- factor(raw_data$SR_Form)
raw_data$Measure_Type <- factor(raw_data$Measure_Type)
raw_data$Year <- as.numeric(raw_data$Year) #removes decimal added, introduces NAs, corrected in next line

raw_data <- raw_data %>% 
  mutate(Year = as.character(ifelse(is.na(Year), "Unpublished", raw_data$Year)))

raw_data <- raw_data %>% 
  mutate(slab=paste0(paste(paste(raw_data$Authors, raw_data$Year, sep=", "), raw_data$N,  sep=" (n = "), ")"))
```

## Calculate Pearson correlations from Spearman correlations
```{r}
#Originally Spearman correlations approximated to Pearson correlations as per Gilpin 1993 (DOI: 10.1177/0013164493053001007) [rounded to 2 decimal places]

#Following review, Spearman correlations apporximated to Pearson correlations as Per
#Rupinski, M. T., & Dunlap, W. P. (1996). Approximating Pearson productmoment correlations from Kendall’s tau and Spearman’s rho. Educa- tional and Psychological Measurement, 56, 419–429. 

# r = 2*sin(r_s*(\frac{\pi}{6}))

#Resulted in very minor changes.

raw_data <- raw_data %>%
  mutate(Correlation_r = as.numeric(case_when(effect_ID == "P10S4C4" ~ 0.4158, #r_s = 0.4        
                                  effect_ID == "P10S6C6" ~ 0.4362, #r_s = 0.42 
                                  effect_ID == "P13S1C1" ~ 0.1046, #r_s = 0.1
                                  effect_ID == "P13S1C2" ~ 0.3128, #r_s = 0.3
                                  effect_ID == "P23S1C1" ~ 0.5277, #r_s = 0.51
                                  effect_ID == "P24S1C2" ~ 0.3747, #r_s = 0.362
                                  effect_ID == "P24S1C1" ~ 0.3850, #r_s = 0.37
                                  effect_ID == "P25S1C1" ~ 0.2153, #r_s = 0.206
                                  effect_ID == "P34S1C1" ~ 0.3953, #r_s = 0.38
                                  effect_ID == "P37S1C1" ~ 0.3969, #r_s = 0.381562
                                  effect_ID == "P37S1C2" ~ 0.3018, #r_s = 0.28938
                                  effect_ID == "P37S2C5" ~ 0.3252, #r_s = 0.31196
                                  effect_ID == "P37S2C6" ~ 0.1912, #r_s = 0.1828896
                                  effect_ID == "P37S1C3" ~ 0.1840, #r_s = 0.17596
                                  effect_ID == "P37S1C4" ~ 0.0129, #r_s = 0.01238
                                  effect_ID == "P37S2C7" ~ 0.5721, #r_s = 0.55409
                                  effect_ID == "P37S2C8" ~ 0.2781, #r_s = 0.26647
                                  effect_ID == "P39S1C1" ~ 0.2994, #r_s = 0.287
                                  effect_ID == "P44S1C1" ~ 0.5247, #r_s = 0.507
                                  TRUE ~ as.numeric(Correlation_r))))
```

############## Section 3: Create Datasets ############## 

```{r}
# Dataset 1: For correlational analysis 1 (use)
use_corr_data <- raw_data %>% filter(`use-cor-analysis` == "Y")

# Dataset 2: For correlational analysis 2 (prob use)
prob_use_corr_data <- raw_data %>% filter(`prob-cor-analysis`== "Y")

# Dataset 3: For analysis of measurement 'accuracy'
acc_data <- raw_data %>% filter(`under-over-analysis` == "Y")
```

# Data set descriptives
```{r}
# overall sample size
raw_data %>% summarise(tot_n = sum(N)) 
```

### Use cor descriptives
```{r}
n_distinct(use_corr_data$Paper_ID)
n_distinct(use_corr_data$Study_ID) 
use_corr_data %>% summarise(tot_n = sum(N)) 

use_corr_data %>% summarise(mean_n = mean(N),
                            sd_n = sd(N),
                            median_n = median(N),
                            min_n = min(N),
                            max_n = max(N))

use_corr_data %>% group_by(Population_Type) %>% tally()
```

```{r}
use_corr_data %>% group_by(Sampling_Category) %>% tally()
```

```{r}
use_corr_data %>% group_by(Log_Collection_category) %>% tally()
```

### prob use cor descriptives
```{r}
n_distinct(prob_use_corr_data$Paper_ID)
n_distinct(prob_use_corr_data$Study_ID) 
prob_use_corr_data %>% summarise(tot_n = sum(N)) 

prob_use_corr_data %>% summarise(mean_n = mean(N),
                            sd_n = sd(N),
                            median_n = median(N),
                            min_n = min(N),
                            max_n = max(N))

prob_use_corr_data %>% group_by(Population_Type) %>% tally()
```
```{r}
prob_use_corr_data %>% group_by(Sampling_Category) %>% tally()
```

```{r}
prob_use_corr_data %>% group_by(Log_Collection_category) %>% tally()
```

### acc, under/over descriptives
```{r}
n_distinct(acc_data$Paper_ID)
n_distinct(acc_data$Study_ID) 
acc_data %>% summarise(tot_n = sum(N)) 

acc_data %>% summarise(mean_n = mean(N),
                            sd_n = sd(N),
                            median_n = median(N),
                            min_n = min(N),
                            max_n = max(N))

acc_data %>% group_by(Population_Type) %>% tally()
```

```{r}
acc_data %>% group_by(Sampling_Category) %>% tally()
```

```{r}
acc_data %>% group_by(Log_Collection_category) %>% tally()
```


############## Section 4: Effect Size Calculations ############## 

## Use correlations
```{r}
use_corr_data <- escalc(measure="ZCOR", ri=Correlation_r, ni=N,data=use_corr_data, slab=paste(Authors, Year, sep=", ")) 
```

## problematic use correlations
```{r}
prob_use_corr_data <- escalc(measure="ZCOR", ri=Correlation_r, ni=N, data=prob_use_corr_data, slab=paste(Authors, Year, sep=", "))
```

## under-over ROMC effect size
```{r}
acc_data <- escalc(measure = "ROMC", m1i=SR_Mean, m2i=Log_Mean, sd1i = SR_SD, sd2i = Log_SD, ni=N, ri=Correlation_r, data=acc_data)
```

# Export clean data sets
```{r}
#Export data to csv
write_csv(use_corr_data, "clean_data/use_corr_data.csv")
write_csv(prob_use_corr_data, "clean_data/prob_use_corr_data.csv")
write_csv(acc_data, "clean_data/acc_data.csv")

#Export data to RDS
saveRDS(use_corr_data, file = "clean_data/use_corr_data.rds")
saveRDS(prob_use_corr_data, file = "clean_data/prob_use_corr_data.rds")
saveRDS(acc_data, file = "clean_data/acc_data.rds")
```

############## Section 5: H1 RE model: use-correlations ############## 

First calculate random effects model with metafor (used for visualisation). After this, use robumeta::robu to calculate model with RVE (using correlational weighting scheme).

```{r}
h1_model <- rma.uni(yi=yi, vi = vi, data=use_corr_data, level = 95, digits = 7)
h1_model
```

# H1 model z to r conversion (with metafor)
```{r}
h1_ztor_model <- predict(h1_model, digits=7, transf = transf.ztor) 
h1_ztor_model
```

# Use robu to get RVE (using CORR for model weights)
```{r}
H1_model_robu <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data)

H1_model_robu #note, these have not been transformed from z to r yet.

#transform
H1_model_robu_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(H1_model_robu$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(H1_model_robu$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(H1_model_robu$reg_table$CI.U)),
                                p.val = as.numeric(H1_model_robu$reg_table$prob)))
H1_model_robu_results
```

# Equivalence test for overall analysis
```{r}
#first need to convert from r to d as TOSTmeta is only compatible with Cohen's d at present. This will result in some loss of precision but, in the context of this analysis, this is acceptable and won't impact the overall outcome.

#lower confidence interval
lower_conf <- (2*H1_model_robu_results$CI.L)/(sqrt(1-H1_model_robu_results$CI.L^2))

#upper confidence interval
upper_conf <- (2*H1_model_robu_results$CI.U)/(sqrt(1-H1_model_robu_results$CI.U^2))

#effect size
ES_r_to_d <- (2*H1_model_robu_results$r)/(sqrt(1-H1_model_robu_results$r^2)) 

# lower equivalence bound
lower_bound <- (2*-0.1)/(sqrt(1-(-0.1)^2)) #-0.2010076

#upper equivalence bound
upper_bound <- (2*0.1)/(sqrt(1-0.1^2)) # 0.2010076

#Need to calculate the standard error from the CIs --> (upper CI- lower CI)/(2*1.96)
es.se <- (upper_conf - lower_conf)/(2*1.96) 

TOSTmeta(ES=ES_r_to_d, se = es.se, low_eqbound_d = lower_bound, high_eqbound_d = upper_bound, alpha = 0.05)
```
# Test for small study bias
```{r}
funnel(h1_model)
```

# Eggers regression test incorporating robust variance estimation (RVE)

Code adapted from: Evaluating Meta-Analytic Methods to Detect Selective Reporting in the Presence of Dependent Effect Sizes (Rodgers and Pustejovsky). Available at: https://osf.io/preprints/metaarxiv/vqp8u/ (peer-reviewed DOI: 10.1037/met0000300). Code https://osf.io/7ak2m/?view_only=e74f9ddad3834e0e8c0bae9ef6b0441c

First create function for the analysis
```{r}
robu_func <- function(formula, dat, fit){
  robu_model <- robu(formula, data = dat, studynum = Study_ID, var.eff.size = vi, 
                     modelweights = "CORR", rho = 0.8, small = TRUE)
  robu_results <- with(robu_model, data.frame(fit = fit, 
                                              beta = as.numeric(robu_model$reg_table$b.r[2]), 
                                              se = as.numeric(robu_model$reg_table$SE[2]), 
                                              p_nomissing = pt(as.numeric(robu_model$reg_table$t[2]), 
                                                        as.numeric(robu_model$reg_table$dfs[2]), 
                                                        lower.tail = FALSE)))
  return(robu_results)
  
}
```

# Run Egger Sandwich Test
```{r}
egg_sndwich_se <- robu_func(formula = yi ~  1 + sqrt(vi), dat = use_corr_data, fit = "RVE")
egg_sndwich_se
```

# Contour enhanced funnel plot
Later in the code a combined, paneled version for all analyses is produced
```{r}
#export to pdf
pdf(file='figures/use_cor_funnel.pdf', height=10, width=12)
cefp <- funnel(h1_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
               legend=TRUE)   
dev.off() 

#export to low res png
png('figures/use_cor_funnel_low_res.png',units="in", height=10, width=12, res=300)
cefp <- funnel(h1_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
               legend=TRUE)   
dev.off() 

#export to high res png
png('figures/use_cor_funnel_high_res.png',units="in", height=10, width=12, res=800)
cefp <- funnel(h1_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
               legend=TRUE)   
dev.off() 
```

## check for outlier with influence test
Note: this approach does not currently work with RVE in either metafor or robumeta.
```{r}
inf <- influence(h1_model)
print(inf)
```

# Leave one out sensitivity analysis 
Note, this does not account for RVE. Therefore, the following chunk conducts the analysis without the identified outlier incorporating RVE.
```{r}
leave1out(h1_model, transf = transf.ztor)
```

```{r}
use_corr_data_no_outlier <- use_corr_data %>% filter(effect_ID != "P15S1C2")

use_cor_no_outlier_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_no_outlier)

use_cor_no_outlier_model #note, these have not been transformed from z to r yet.

#transform
use_cor_no_outlier_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_no_outlier_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_no_outlier_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_no_outlier_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_no_outlier_model$reg_table$prob)))
use_cor_no_outlier_model_results

rm(use_corr_data_no_outlier, use_cor_no_outlier_model_results) #remove redundant dataframe
```

#Sensitivity analysis for correlation type (excluding sparman correlations)
```{r}
use_corr_data_no_spearman <- use_corr_data %>% filter(!effect_ID %in% c("P10S4C4", "P10S6C6", "P13S1C1", "P13S1C2", "P23S1C1", "P24S1C2", "P24S1C1", "P25S1C1", "P34S1C1", "P37S1C1", "P37S1C2", "P37S2C5", "P37S2C6", "P37S1C3", "P37S1C4", "P37S2C7", "P37S2C8", "P39S1C1", "P44S1C1"))

use_corr_data_no_spearman_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_no_spearman)

use_corr_data_no_spearman_model #note, these have not been transformed from z to r yet.

#transform
use_corr_data_no_spearman_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_no_spearman_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_no_spearman_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_no_spearman_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_no_spearman_model$reg_table$prob)))
use_corr_data_no_spearman_model_results

rm(use_corr_data_no_spearman, use_corr_data_no_spearman_model_results) #remove redundant dataframe
```

# sensitvity analysis for publication status:
```{r}
use_corr_data_Pub <- use_corr_data %>%  filter(Source_Type == "Published")

use_cor_published_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Pub)
use_cor_published_model

#transform
use_cor_published_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_published_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_published_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_published_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_published_model$reg_table$prob)))
use_cor_published_model_results

rm(use_corr_data_Pub, use_cor_published_model_results)
```

```{r}
use_corr_data_UnPub <- use_corr_data %>%  filter(Source_Type == "Unpublished")

use_cor_unpub_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_UnPub)
use_cor_unpub_model

#transform
use_cor_unpub_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_unpub_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_unpub_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_unpub_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_unpub_model$reg_table$prob)))
use_cor_unpub_model_results

rm(use_corr_data_UnPub, use_cor_unpub_model_results)
```

# moderator analysis for publication status
```{r}
use_cor_pub_status_model <- robu(formula = yi ~ Source_Type, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data)
use_cor_pub_status_model

#transform
use_cor_pub_status_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_pub_status_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_pub_status_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_pub_status_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_pub_status_model$reg_table$prob)))
use_cor_pub_status_model_results

rm(use_cor_pub_status_model_results)
```

## Sensitivity analysis excluding digitised study
```{r}
use_corr_data_non_digitised <- use_corr_data %>%  filter(effect_ID != "P17S1C1")

use_cor_non_digitised_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_non_digitised)
use_cor_non_digitised_model

#transform
use_cor_non_digitised_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_non_digitised_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_non_digitised_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_non_digitised_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_non_digitised_model$reg_table$prob)))
use_cor_non_digitised_model_results

rm(use_corr_data_non_digitised, use_cor_non_digitised_model_results)
```

## Sensitivity analysis excluding additionally included effect
```{r}
use_corr_data_non_late <- use_corr_data %>%  filter(Study_ID != "P47S1")

use_cor_non_late_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_non_late)
use_cor_non_digitised_model

#transform
use_cor_non_late_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_non_late_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_non_late_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_non_late_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_non_late_model$reg_table$prob)))
use_cor_non_late_model_results

rm(use_corr_data_non_late, use_cor_non_late_model_results)
```

# Produce forest plot for H1
The forest plot is produced and exported in 3 formats: pdf, low-res png and high-res png.

## function to produce the forest plot
```{r}
produce_use_cor_forest <- function(){

forest(h1_model, 
       atransf=transf.ztor,
       xlim=c(-3.9,3), alim=c(-0.5, 2),
       header="Author(s) and Year",
       slab=use_corr_data$slab, 
       at=transf.rtoz(c(-0.4, 0, .5, .9)),
       order=order(transf.ztor(use_corr_data$yi)), #order by effect size
       xlab="Correlation Coefficient",
       mlab = "",
       addfit = FALSE,
       ilab=as.character(use_corr_data$medium), ilab.xpos = -0.9)

addpoly(x = 0.398, ci.lb = 0.345, ci.ub = 0.449, atransf=transf.ztor, row=-1, mlab="", cex=1)

abline(h = 0.45)

text(-0.9, 68, "Medium", font=2)
#text(-3.9, -1, pos=4, "RE Model", font=2)
text(-3.9, -1, pos=4, "RE Model with RVE (using correlational weighting scheme)", font=2)

segments(transf.rtoz(0.5), -5, transf.rtoz(0.5), 67, lty="dotted") #extra line at r=0.5
}
```

### Export as pdf
```{r}
pdf(file='figures/use_cor_forest.pdf', height=13.5, width=10)
par(mar=c(3.5,3.5,0.2,1.5))

produce_use_cor_forest()

par(font=2)
dev.off()
```

### Export as png (low res)
```{r}
png(file='figures/use_cor_forest_low_res.png', units = "in", height=13.5, width=10, res=300)
par(mar=c(3.5,3.5,0.2,1.5))

produce_use_cor_forest()

par(font=2)
dev.off()
```

### Export as png (high res)
```{r}
png(file='figures/use_cor_forest_high_res.png', units = "in", height=13.5, width=10, res=800)
par(mar=c(3.5,3.5,0.2,1.5))

produce_use_cor_forest()

par(font=2)
dev.off()
```

############## Section 6: RQ1: Moderators of H1 ############## 

For all moderators, first check if there are 4 observations at each moderator level

#RQ1a: medium as moderator (Computer, Phone, Social media, Internet, Games):
```{r}
use_corr_data %>% dplyr::select(medium) %>% group_by(medium) %>% tally()
```

Only select the moderator levels for which there are 4 or more observations
```{r}
medium_data <- use_corr_data %>% 
  filter(medium == "Phone" | medium == "Social Media")

macat(es=yi, var=vi, mod=medium, data=medium_data, method="random", ztor=TRUE)
```
Because there are only 2 levels, not conducting pairwise comparison (in the protocol this is specified for all moderators with more than two levels)

```{r}
use_corr_data_Phone <- use_corr_data %>%  filter(medium == "Phone")

use_cor_phone_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Phone)
use_cor_phone_model

#transform
use_cor_phone_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_phone_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_phone_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_phone_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_phone_model$reg_table$prob)))
use_cor_phone_model_results

rm(use_corr_data_Phone, use_cor_phone_model_results)
```

```{r}
use_corr_data_Social_Media <- use_corr_data %>%  filter(medium == "Social Media")

use_cor_social_media_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Social_Media)
use_cor_social_media_model

#transform
use_cor_social_media_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_social_media_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_social_media_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_social_media_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_social_media_model$reg_table$prob)))
use_cor_social_media_model_results

rm(use_corr_data_Social_Media, use_cor_social_media_model_results)
```

### Model excluding gaming, computers, and internet
```{r}
use_cor_medium_excluding_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = medium_data)
use_cor_medium_excluding_model

#transform
use_cor_medium_excluding_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_medium_excluding_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_medium_excluding_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_medium_excluding_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_medium_excluding_model$reg_table$prob)))
use_cor_medium_excluding_model_results
```

Moderator model
```{r}
use_cor_medium_excluding_moderator_model <- robu(formula = yi ~ medium, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = medium_data)
use_cor_medium_excluding_moderator_model

#transform
use_cor_medium_excluding_moderator_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_medium_excluding_moderator_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_medium_excluding_moderator_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_medium_excluding_moderator_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_medium_excluding_moderator_model$reg_table$prob)))
use_cor_medium_excluding_moderator_model_results

rm(medium_data, use_cor_medium_excluding_moderator_model_results)
```

# RQ1b: Self-report form as moderator (single estimate vs. scale):
```{r}
use_corr_data %>% dplyr::select(SR_Form) %>% group_by(SR_Form) %>% tally()
```
```{r}
macat(es=yi, var=vi, mod=SR_Form, data=use_corr_data, method="random", ztor=TRUE)
```

#Individual levels with RVE
```{r}
use_corr_data_Single <- use_corr_data %>% filter(SR_Form == "SINGLE")

use_cor_single_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Single)
use_cor_single_model

#transform
use_cor_single_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_single_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_single_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_single_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_single_model$reg_table$prob)))
use_cor_single_model_results

rm(use_corr_data_Single, use_cor_single_model_results)
```

```{r}
use_corr_data_Scale <- use_corr_data %>% filter(SR_Form == "SCALE")

use_cor_scale_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Scale)
use_cor_scale_model

#transform
use_cor_scale_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_scale_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_scale_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_scale_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_scale_model$reg_table$prob)))
use_cor_scale_model_results

rm(use_corr_data_Scale, use_cor_scale_model_results)
```

Run moderator model
```{r}
use_cor_self_report_form_model <- robu(formula = yi ~ SR_Form, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data)
use_cor_self_report_form_model

#transform
use_cor_self_report_form_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_self_report_form_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_self_report_form_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_self_report_form_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_self_report_form_model$reg_table$prob)))
use_cor_self_report_form_model_results
```

#RQ1c: Category of media use as moderator (volume or duration of usage):
```{r}
use_corr_data %>% dplyr::select(Measure_Type) %>% group_by(Measure_Type) %>% tally()
```
```{r}
macat(es=yi, var=vi, mod=Measure_Type, data=use_corr_data, method="random", ztor=TRUE) 
```

```{r}
use_corr_data_Duration <- use_corr_data %>% filter(Measure_Type == "Duration")

use_cor_duration_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Duration)
use_cor_duration_model

#transform
use_cor_duration_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_duration_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_duration_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_duration_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_duration_model$reg_table$prob)))
use_cor_duration_model_results

rm(use_corr_data_Duration, use_cor_duration_model_results)
```

```{r}
use_corr_data_Volume <- use_corr_data %>% filter(Measure_Type == "Volume")

use_cor_volume_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_Volume)
use_cor_volume_model

#transform
use_cor_volume_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_cor_volume_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_volume_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_volume_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_volume_model$reg_table$prob)))
use_cor_volume_model_results

rm(use_corr_data_Volume, use_cor_volume_model_results)
```

```{r}
use_cor_self_report_category_model <- robu(formula = yi ~ Measure_Type, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data)
use_cor_self_report_category_model

#transform
use_cor_self_report_category_model_results <- data.frame(cbind(est = as.numeric(psych::fisherz2r(use_cor_self_report_category_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_cor_self_report_category_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_cor_self_report_category_model$reg_table$CI.U)),
                                p.val = as.numeric(use_cor_self_report_category_model$reg_table$prob)))
use_cor_self_report_category_model_results
```

# Additional post hoc exploratory moderator analyses

## Population

### subgroups

```{r}
use_corr_data_pop_adults <- use_corr_data %>% filter(Population_Type == "adults")
use_corr_data_pop_student <- use_corr_data %>% filter(Population_Type == "student")
use_corr_data_pop_general <- use_corr_data %>% filter(Population_Type == "general")
use_corr_data_pop_unknown <- use_corr_data %>% filter(Population_Type == "unknown")

use_corr_data_pop_adults_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_pop_adults)
use_corr_data_pop_student_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_pop_student)
use_corr_data_pop_general_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_pop_general)
use_corr_data_pop_unknown_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_pop_unknown)
```

```{r}
use_corr_data_pop_adults_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_pop_adults_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_pop_adults_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_pop_adults_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_pop_adults_model$reg_table$prob)))
use_corr_data_pop_adults_model_results
```

```{r}
use_corr_data_pop_student_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_pop_student_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_pop_student_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_pop_student_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_pop_student_model$reg_table$prob)))
use_corr_data_pop_student_model_results
```

```{r}
use_corr_data_pop_general_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_pop_general_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_pop_general_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_pop_general_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_pop_general_model$reg_table$prob)))
use_corr_data_pop_general_model_results
```

```{r}
use_corr_data_pop_unknown_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_pop_unknown_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_pop_unknown_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_pop_unknown_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_pop_unknown_model$reg_table$prob)))
use_corr_data_pop_unknown_model_results
```

```{r}
rm(use_corr_data_pop_adults, use_corr_data_pop_student, use_corr_data_pop_general, use_corr_data_pop_unknown,
   use_corr_data_pop_adults_model_results, use_corr_data_pop_student_model_results, use_corr_data_pop_student_model_results, use_corr_data_pop_unknown_model_results)
```

### moderator analysis
```{r}
use_corr_data_population <- use_corr_data %>%  filter(Population_Type != "adolescents")

pop.mr <- robu(formula = yi ~ Population_Type,
               data = use_corr_data_population, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

pop.wald <- Wald_test(obj = pop.mr, 
                      constraints = 2:4, 
                      vcov = "CR2")

pop.wald
rm(use_corr_data_population)
```

## Sampling/data collection design

### subgroups
```{r}
use_corr_data_sampling_donation <- use_corr_data %>% filter(Sampling_Category == "data_donation")
use_corr_data_sampling_tracking <- use_corr_data %>% filter(Sampling_Category == "direct_tracking")
use_corr_data_sampling_supplied <- use_corr_data %>% filter(Sampling_Category == "supplied_data")

use_corr_data_sampling_donation_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_sampling_donation)
use_corr_data_sampling_tracking_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_sampling_tracking)
use_corr_data_sampling_supplied_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_sampling_supplied)
```

```{r}
use_corr_data_sampling_donation_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_sampling_donation_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_sampling_donation_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_sampling_donation_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_sampling_donation_model$reg_table$prob)))
use_corr_data_sampling_donation_model_results
```

```{r}
use_corr_data_sampling_tracking_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_sampling_tracking_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_sampling_tracking_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_sampling_tracking_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_sampling_tracking_model$reg_table$prob)))
use_corr_data_sampling_tracking_model_results
```

```{r}
use_corr_data_sampling_supplied_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_sampling_supplied_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_sampling_supplied_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_sampling_supplied_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_sampling_supplied_model$reg_table$prob)))
use_corr_data_sampling_supplied_model_results
```

```{r}
rm(use_corr_data_sampling_donation, use_corr_data_sampling_donation_model_results, use_corr_data_sampling_tracking, use_corr_data_sampling_tracking_model_results, use_corr_data_sampling_supplied, use_corr_data_sampling_supplied_model_results)
```


### moderator analysis (3 levels = omnibus test)
```{r}
sampling.mr <- robu(formula = yi ~ Sampling_Category,
               data = use_corr_data, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

sampling.wald <- Wald_test(obj = sampling.mr, 
                      constraints = 2:3, 
                      vcov = "CR2")

sampling.wald
```


## Log collection method

### subgroups
```{r}
use_corr_data_logging_built <- use_corr_data %>% filter(Log_Collection_category == "built_in")
use_corr_data_logging_custom <- use_corr_data %>% filter(Log_Collection_category == "custom_built_for_research")
use_corr_data_logging_operator <- use_corr_data %>% filter(Log_Collection_category == "operator")
use_corr_data_logging_third <- use_corr_data %>% filter(Log_Collection_category == "third_party")

use_corr_data_logging_built_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_logging_built)
use_corr_data_logging_custom_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_logging_custom)
use_corr_data_logging_operator_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_logging_operator)
use_corr_data_logging_third_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = use_corr_data_logging_third)
```

```{r}
use_corr_data_logging_built_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_logging_built_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_logging_built_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_logging_built_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_logging_built_model$reg_table$prob)))
use_corr_data_logging_built_model_results
```

```{r}
use_corr_data_logging_custom_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_logging_custom_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_logging_custom_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_logging_custom_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_logging_custom_model$reg_table$prob)))
use_corr_data_logging_custom_model_results
```

```{r}
use_corr_data_logging_operator_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_logging_operator_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_logging_operator_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_logging_operator_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_logging_operator_model$reg_table$prob)))
use_corr_data_logging_operator_model_results
```

```{r}
use_corr_data_logging_third_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_corr_data_logging_third_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_corr_data_logging_third_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_corr_data_logging_third_model$reg_table$CI.U)),
                                p.val = as.numeric(use_corr_data_logging_third_model$reg_table$prob)))
use_corr_data_logging_third_model_results
```

### moderator analysis (4 levels = omnibus test)
```{r}
use_corr_data_log_collection_category <- use_corr_data %>%  filter(Log_Collection_category != "other")

log.mr <- robu(formula = yi ~ Log_Collection_category,
               data = use_corr_data_log_collection_category, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

log.wald <- Wald_test(obj = log.mr, 
                      constraints = 2:4, 
                      vcov = "CR2")

log.wald
rm(use_corr_data_log_collection_category)
```

## Final additional post hoc omnibus moderator analysis

```{r}
use_corr_data_dropped <- use_corr_data %>%  filter(medium == "Social Media" | medium == "Phone")

use_omni.mr <- robu(formula = yi ~ medium + SR_Form + Measure_Type,
               data = use_corr_data_dropped, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

use_omni.mr

use_omni.mr_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(use_omni.mr$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(use_omni.mr$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(use_omni.mr$reg_table$CI.U)),
                                p.val = as.numeric(use_omni.mr$reg_table$prob)))
use_omni.mr_results

use_omni.wald <- Wald_test(obj = use_omni.mr, 
                      constraints = 2:4, 
                      vcov = "CR2")

use_omni.wald
```






############## Section 7: RQ2: under- or over-reporting ############## 

## proportion under/accurate/over

We used a margin of error of 5% or more above the tracked measure to indicate over-reporting, 5% or more below to indicate under-reporting, and mean estimates within 5% of the log-based measure to be accurate. 

```{r}
acc_data <- acc_data %>% 
  mutate(acc = case_when(SR_Mean > (Log_Mean + 0.05*Log_Mean) ~ "over",
                                    SR_Mean < (Log_Mean - 0.05*Log_Mean) ~ "under",
                                    TRUE ~ "accurate"))

acc_data %>% 
  group_by(acc) %>% 
  summarise(n = n()) %>%
  mutate((freq = n / sum(n))*100)
```

## RE model
First calculate random effects model with metafor (used for visualisation). After this, use robumeta::robu to calculate model with RVE (using correlational weighting scheme).
```{r}
rq2_model <- rma.uni(yi=yi, vi = vi, data=acc_data, level = 95, digits = 7)
rq2_model
```

# Use robu to calculate RVE
```{r}
rq2_model_robu <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data)

rq2_model_robu #note, these have not been transformed from log to exp

#back-transform
rq2_model_results <- data.frame(cbind(RR = as.numeric(exp(rq2_model_robu$reg_table$b.r)),
                                CI.L = as.numeric(exp(rq2_model_robu$reg_table$CI.L)),
                                CI.U = as.numeric(exp(rq2_model_robu$reg_table$CI.U)),
                                p.val = as.numeric(rq2_model_robu$reg_table$prob)))
rq2_model_results
```

# Test for small study bias
```{r}
funnel(rq2_model)
```
# Eggers regression test incorporating robust variance estimation (RVE)
```{r}
egg_sndwich_se <- robu_func(formula = yi ~  1 + sqrt(vi), dat = acc_data, fit = "RVE")
egg_sndwich_se
```

# Contour enhanced funnel plot:
```{r}
#export to pdf
pdf(file='figures/acc_funnel.pdf', height=10, width=12)
cefp <- funnel(rq2_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = exp,
               legend=TRUE)   
dev.off() 

#export to low res png
png('figures/acc_funnel_low_res.png',units="in", height=10, width=12, res=300)
cefp <- funnel(rq2_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = exp,
               legend=TRUE)   
dev.off() 

#export to high res png
png('figures/acc_funnel_high_res.png',units="in", height=10, width=12, res=800)
cefp <- funnel(rq2_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = exp,
               legend=TRUE)   
dev.off() 
```

# check for outlier with influence test
Note: this approach does not currently work with RVE in either metafor or robumeta.
```{r}
inf <- influence(rq2_model)
print(inf)
```

# Leave one out sensitivity analysis 
Note, this does not account for RVE. Therefore, the following chunk conducts the analysis without the identified outlier incorporating RVE.
```{r}
leave1out(rq2_model, transf = exp)
```

# excluding outlier and account for RVE
```{r}
acc_data_no_outlier <- acc_data %>% filter(effect_ID != "P15S1C2")

acc_no_outlier_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_no_outlier)
acc_no_outlier_model #note, these have not been transformed from log to exp yet

#back-transform
acc_no_outlier_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_no_outlier_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_no_outlier_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_no_outlier_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_no_outlier_model$reg_table$prob)))
acc_no_outlier_model_results

rm(acc_data_no_outlier, acc_no_outlier_model_results)
```

#Sensitivity analysis for correlation type (excluding sparman correlations)
```{r}
acc_data_no_spearman <- acc_data %>% filter(!effect_ID %in% c("P10S4C4", "P10S6C6", "P13S1C1", "P13S1C2", "P23S1C1", "P24S1C2", "P24S1C1", "P25S1C1", "P34S1C1", "P37S1C1", "P37S1C2", "P37S2C5", "P37S2C6", "P37S1C3", "P37S1C4", "P37S2C7", "P37S2C8", "P39S1C1", "P44S1C1"))

acc_no_spearman_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_no_spearman)

acc_no_spearman_model #note, these have not been transformed from z to r yet.

#transform
acc_no_spearman_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_no_spearman_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_no_spearman_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_no_spearman_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_no_spearman_model$reg_table$prob)))
acc_no_spearman_model_results

rm(acc_data_no_spearman, acc_no_spearman_model_results) #remove redundant dataframe
```

# sensitvity analysis for publication status:
```{r}
acc_data_Pub <- acc_data %>%  filter(Source_Type == "Published")

acc_published_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_Pub)
acc_published_model

#back-transform
acc_published_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_published_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_published_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_published_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_published_model$reg_table$prob)))
acc_published_model_results

rm(acc_data_Pub, acc_published_model_results)
```

```{r}
acc_data_UnPub <- acc_data %>%  filter(Source_Type == "Unpublished")

acc_unpublished_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_UnPub)
acc_unpublished_model

#back-transform
acc_unpublished_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_unpublished_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_unpublished_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_unpublished_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_unpublished_model$reg_table$prob)))
acc_unpublished_model_results

rm(acc_data_UnPub, acc_unpublished_model_results)
```

#moderator analysis for publication status
```{r}
acc_publication_status_moderator_model <- robu(formula = yi ~ Source_Type, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data)
acc_publication_status_moderator_model
```

```{r}
#back-transform
acc_publication_status_moderator_model_results <- data.frame(cbind(est = as.numeric(exp(acc_publication_status_moderator_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_publication_status_moderator_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_publication_status_moderator_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_publication_status_moderator_model$reg_table$prob)))
acc_publication_status_moderator_model_results
rm(acc_publication_status_moderator_model_results)
```
## Sensitivity analysis excluding effect of two digitised studies

```{r}
acc_data_non_digitised <- acc_data %>% 
  filter(plot_digitised == "N")

acc_non_digitised_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_non_digitised)
acc_non_digitised_model

#back-transform
acc_non_digitised_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_non_digitised_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_non_digitised_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_non_digitised_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_non_digitised_model$reg_table$prob)))
acc_non_digitised_model_results

rm(acc_data_non_digitised, acc_non_digitised_model_results)
```

# Forest plot
Forest plot function
```{r}
produce_acc_forest_plot <- function(){

forest(rq2_model, 
       transf=exp, 
       alim=c(0, 20), xlim=c(-35,35),
       refline=1,
       slab=acc_data$slab,
       mlab = "",
       header="Author(s) and Year",
       addfit = FALSE,
       ilab=as.character(acc_data$Measure_Type), ilab.xpos = -5,
       order="obs") 

addpoly(x = rq2_model_robu$reg_table$b.r, ci.lb = rq2_model_robu$reg_table$CI.L, ci.ub = rq2_model_robu$reg_table$CI.U, transf = exp, row=-0.8, mlab="", cex=1)
abline(h=0.45)
  
text(-5, 51, "Use Category", font=2)

text(-35, -0.8, pos=4, "RE Model with RVE (using correlational weighting scheme)", font=2)

}

```

```{r}
produce_acc_forest_plot_log <- function(){

forest(rq2_model, 
       #transf=exp, 
       atransf=exp,
       alim=c(-1.5, 4), xlim=c(-10,7),
       refline=0,
       slab=acc_data$slab,
       mlab = "",
       header="Author(s) and Year",
       addfit = FALSE,
       ilab=as.character(acc_data$Measure_Type), ilab.xpos = -2.7,
       order="obs") 

addpoly(x = rq2_model_robu$reg_table$b.r, ci.lb = rq2_model_robu$reg_table$CI.L, ci.ub = rq2_model_robu$reg_table$CI.U, row=-0.8, mlab="", cex=1, atransf=exp)

abline(h=0.45)
  
text(-2.7, 51, "Use Category", font=2)

text(-10, -0.8, pos=4, "RE Model with RVE (using correlational weighting scheme)", font=2)

}

```

Export PDF-log
```{r}
pdf(file='figures/acc_log_forest.pdf', height=12, width=10)
par(mar=c(4,3.6,0.2,1.5))

produce_acc_forest_plot_log()

par(font=2)
dev.off()
```

Export PDF
```{r}
pdf(file='figures/acc_forest.pdf', height=12, width=10)
par(mar=c(4,3.6,0.2,1.5))

produce_acc_forest_plot()

par(font=2)
dev.off()
```

Export as png (low res)
```{r}
png(file='figures/acc_forest_low_res.png', units = "in", height=13.5, width=10, res=300)
par(mar=c(3.5,3.5,0.2,1.5))

produce_acc_forest_plot()

par(font=2)
dev.off()
```

Export as png (low res)
```{r}
png(file='figures/acc_forest_log_low_res.png', units = "in", height=13.5, width=10, res=300)
par(mar=c(3.5,3.5,0.2,1.5))

produce_acc_forest_plot_log()

par(font=2)
dev.off()
```

Export as png (high res)
```{r}
png(file='figures/acc_forest_log_high_res.png', units = "in", height=13.5, width=10, res=800)
par(mar=c(3.5,3.5,0.2,1.5))

produce_acc_forest_plot_log()

par(font=2)
dev.off()
```

Export as png (high res)
```{r}
png(file='figures/acc_forest_high_res.png', units = "in", height=13.5, width=10, res=800)
par(mar=c(3.5,3.5,0.2,1.5))

produce_acc_forest_plot()

par(font=2)
dev.off()
```

############## Section 8: RQ3: moderators of RQ2 ############## 

#RQ3a medium as moderator
```{r}
acc_data %>% dplyr::select(medium) %>% group_by(medium) %>% tally()
```

```{r}
acc_data_phone <- acc_data %>% filter(medium == "Phone")

acc_phone_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_phone)
acc_phone_model

#back-transform
acc_phone_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_phone_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_phone_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_phone_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_phone_model$reg_table$prob)))
acc_phone_model_results

rm(acc_data_phone, acc_phone_model_results)
```

```{r}
acc_data_soc_med <- acc_data %>% filter(medium == "Social Media")

acc_socmed_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_soc_med)
acc_socmed_model

#back-transform
acc_socmed_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_socmed_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_socmed_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_socmed_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_socmed_model$reg_table$prob)))
acc_socmed_model_results

rm(acc_data_soc_med, acc_socmed_model_results)
```

#RQ3b category of media use (duration or volume) as moderator
```{r}
acc_data %>% dplyr::select(Measure_Type) %>% group_by(Measure_Type) %>% tally()
```

```{r}
acc_data_duration <- acc_data %>% filter(Measure_Type == "Duration")

acc_duration_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_duration)
acc_duration_model

#back-transform
acc_duration_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_duration_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_duration_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_duration_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_duration_model$reg_table$prob)))
acc_duration_model_results

rm(acc_data_duration, acc_duration_model_results)
```

```{r}
acc_data_volume <- acc_data %>% filter(Measure_Type == "Volume")

acc_volume_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_volume)
acc_volume_model

#back-transform
acc_volume_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_volume_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_volume_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_volume_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_volume_model$reg_table$prob)))
acc_volume_model_results

rm(acc_data_volume, acc_volume_model_results)
```

```{r}
acc_self_report_category_moderator_model <- robu(formula = yi ~ Measure_Type, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data)
acc_self_report_category_moderator_model

#back-transform
acc_self_report_category_moderator_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_self_report_category_moderator_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_self_report_category_moderator_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_self_report_category_moderator_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_self_report_category_moderator_model$reg_table$prob)))
acc_self_report_category_moderator_model_results
rm(acc_self_report_category_moderator_model_results)
```

# Additional post hoc exploratory moderator analyses

## Population [note dropped adolescents as only 2 ESs, dropped unknown as only 1 ES, dropped general as only 3 ESs]

### subgroups
```{r}
acc_data_pop_adults <- acc_data %>% filter(Population_Type == "adults")
acc_data_pop_student <- acc_data %>% filter(Population_Type == "student")
```

```{r}
acc_data_pop_adults_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_pop_adults)
acc_data_pop_adults_model

#back-transform
acc_data_pop_adults_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_pop_adults_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_pop_adults_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_pop_adults_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_pop_adults_model$reg_table$prob)))
acc_data_pop_adults_model_results
```

```{r}
acc_data_pop_student_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_pop_student)
acc_data_pop_student_model

#back-transform
acc_data_pop_student_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_pop_student_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_pop_student_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_pop_student_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_pop_student_model$reg_table$prob)))
acc_data_pop_student_model_results
```

```{r}
rm(acc_data_pop_student_model_results, acc_data_pop_adults_model_results, acc_data_pop_student, acc_data_pop_adults)
```

### moderator analysis [normal moderator analysis]
```{r}
acc_data_pop <- acc_data %>% 
  filter(Population_Type == "adults" | Population_Type == "student")

acc_pop_moderator_model <- robu(formula = yi ~ Population_Type, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_pop)
acc_pop_moderator_model

#back-transform
acc_pop_moderator_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_pop_moderator_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_pop_moderator_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_pop_moderator_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_pop_moderator_model$reg_table$prob)))
acc_pop_moderator_model_results
```

## sampling category [no dropping]

### subgroups
```{r}
acc_data_sampling_donation <- acc_data %>% filter(Sampling_Category == "data_donation")
acc_data_sampling_tracking <- acc_data %>% filter(Sampling_Category == "direct_tracking")
acc_data_sampling_supplied <- acc_data %>% filter(Sampling_Category == "supplied_data")
```

```{r}
acc_data_sampling_donation_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_sampling_donation)
acc_data_sampling_donation_model

#back-transform
acc_data_sampling_donation_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_pop_student_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_sampling_donation_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_sampling_donation_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_sampling_donation_model$reg_table$prob)))
acc_data_sampling_donation_model_results
```

```{r}
acc_data_sampling_tracking_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_sampling_tracking)
acc_data_sampling_tracking_model

#back-transform
acc_data_sampling_tracking_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_sampling_tracking_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_sampling_tracking_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_sampling_tracking_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_sampling_tracking_model$reg_table$prob)))
acc_data_sampling_tracking_model_results
```

```{r}
acc_data_sampling_supplied_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_sampling_supplied)
acc_data_sampling_supplied_model

#back-transform
acc_data_sampling_supplied_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_sampling_supplied_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_sampling_supplied_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_sampling_supplied_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_sampling_supplied_model$reg_table$prob)))
acc_data_sampling_supplied_model_results
```

```{r}
rm(acc_data_sampling_donation_model_results, acc_data_sampling_tracking_model_results, acc_data_sampling_supplied_model_results, acc_data_sampling_donation, acc_data_sampling_tracking, acc_data_sampling_supplied)
```

### moderator analysis
```{r}
sc.mr <- robu(formula = yi ~ Sampling_Category,
               data = acc_data, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

sc.wald <- Wald_test(obj = sc.mr, 
                      constraints = 2:3, 
                      vcov = "CR2")

sc.wald
```

## logging collection method [no dropping]

### subgroups
```{r}
acc_data_lc_built <- acc_data %>% filter(Log_Collection_category == "built_in")
acc_data_lc_custom <- acc_data %>% filter(Log_Collection_category == "custom_built_for_research")
acc_data_lc_operator <- acc_data %>% filter(Log_Collection_category == "operator")
acc_data_lc_third <- acc_data %>% filter(Log_Collection_category == "third_party")
```

```{r}
acc_data_lc_built_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_lc_built)
acc_data_lc_built_model

#back-transform
acc_data_lc_built_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_lc_built_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_lc_built_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_lc_built_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_lc_built_model$reg_table$prob)))
acc_data_lc_built_model_results
```

```{r}
acc_data_lc_custom_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_lc_custom)
acc_data_lc_custom_model

#back-transform
acc_data_lc_custom_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_lc_custom_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_lc_custom_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_lc_custom_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_lc_custom_model$reg_table$prob)))
acc_data_lc_custom_model_results
```

```{r}
acc_data_lc_operator_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_lc_operator)
acc_data_lc_operator_model

#back-transform
acc_data_lc_operator_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_lc_operator_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_lc_operator_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_lc_operator_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_lc_operator_model$reg_table$prob)))
acc_data_lc_operator_model_results
```

```{r}
acc_data_lc_third_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = acc_data_lc_third)
acc_data_lc_third_model

#back-transform
acc_data_lc_third_model_results <- data.frame(cbind(RR = as.numeric(exp(acc_data_lc_third_model$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_data_lc_third_model$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_data_lc_third_model$reg_table$CI.U)),
                                p.val = as.numeric(acc_data_lc_third_model$reg_table$prob)))
acc_data_lc_third_model_results
```

###moderator analysis
```{r}
lc.mr <- robu(formula = yi ~ Log_Collection_category,
               data = acc_data, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

lc.wald <- Wald_test(obj = lc.mr, 
                      constraints = 2:4, 
                      vcov = "CR2")

lc.wald
```

## Final additional post hoc omnibus moderator analysis

```{r}
acc_data_dropped <- use_corr_data %>%  filter(medium == "Social Media" | medium == "Phone")

acc_omni.mr <- robu(formula = yi ~ medium + Measure_Type,
               data = acc_data_dropped, 
               studynum = Study_ID,
               var.eff.size = vi,
               modelweights = "CORR",
               small = TRUE)

acc_omni.mr

acc_omni.mr_results <- data.frame(cbind(RR = as.numeric(exp(acc_omni.mr$reg_table$b.r)),
                                CI.L = as.numeric(exp(acc_omni.mr$reg_table$CI.L)),
                                CI.U = as.numeric(exp(acc_omni.mr$reg_table$CI.U)),
                                p.val = as.numeric(acc_omni.mr$reg_table$prob)))
acc_omni.mr_results

acc_omni.wald <- Wald_test(obj = acc_omni.mr, 
                      constraints = 2:3, 
                      vcov = "CR2")

acc_omni.wald
```

############## Section 9: H1 RE model: prob-use-correlations ############## 
First calculate random effects model with metafor (used for visualisation). After this, use robumeta::robu to calculate model with RVE (using correlational weighting scheme).
```{r}
h2_model <- rma.uni(yi=yi, vi = vi, data=prob_use_corr_data, level = 95, digits = 7)
h2_model
```

# Use robu to get RVE (using CORR for model weights)
```{r}
h2_model_robu <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = prob_use_corr_data)

h2_model_robu #note, these have not been transformed from z to r yet.

#transform
h2_model_robu_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(h2_model_robu$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(h2_model_robu$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(h2_model_robu$reg_table$CI.U)),
                                p.val = as.numeric(h2_model_robu$reg_table$prob)))
h2_model_robu_results
```

# Equivalence test for overall analysis

```{r}
#first need to convert from r to d as TOSTmeta is only compatible with Cohen's d at present. This will result in some loss of precision but, in the context of this analysis, this is acceptable and won't impact the overall outcome.

#lower confidence interval
lower_conf <- (2*h2_model_robu_results$CI.L)/(sqrt(1-h2_model_robu_results$CI.L^2))

#upper confidence interval
upper_conf <- (2*h2_model_robu_results$CI.U)/(sqrt(1-h2_model_robu_results$CI.U^2))

#effect size
ES_r_to_d <- (2*h2_model_robu_results$r)/(sqrt(1-h2_model_robu_results$r^2)) 

# lower equivalence bound
lower_bound <- (2*-0.1)/(sqrt(1-(-0.1)^2)) #-0.2010076

#upper equivalence bound
upper_bound <- (2*0.1)/(sqrt(1-0.1^2)) # 0.2010076

#Need to calculate the standard error from the CIs --> (upper CI- lower CI)/(2*1.96)
es.se <- (upper_conf - lower_conf)/(2*1.96) 

TOSTmeta(ES=ES_r_to_d, se = es.se, low_eqbound_d = lower_bound, high_eqbound_d = upper_bound, alpha = 0.05)
```
# Egger's regression test
```{r}
funnel(h2_model)
```
# Eggers regression test incorporating robust variance estimation (RVE)
```{r}
egg_sndwich_se <- robu_func(formula = yi ~  1 + sqrt(vi), dat = prob_use_corr_data, fit = "RVE")
egg_sndwich_se
```

# Contour enhanced funnel plot:
```{r}
#export to pdf
pdf(file='figures/prob_use_cor_funnel.pdf', height=10, width=12)
cefp <- funnel(h2_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
               legend=TRUE)   
dev.off() 

#export to low res png
png('figures/prob_use_cor_funnel_low_res.png',units="in", height=10, width=12, res=300)
cefp <- funnel(h2_model, level=c(90, 95, 99), 
               shade=c("white", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
               legend=TRUE)   
dev.off() 

#export to high res png
png('figures/prob_use_cor_funnel_high_res.png',units="in", height=10, width=12, res=800)
cefp <- funnel(h2_model, level=c(90, 95, 99), 
               atransf = transf.ztor,
               legend=TRUE)   
dev.off() 
```

## check for outlier with influence test
Note, this does not account for RVE.
```{r}
inf <- influence(h2_model)
print(inf)
```

#Sensitivity analysis for correlation type (excluding sparman correlations)
```{r}
prob_use_corr_data_no_spearman <- prob_use_corr_data %>% filter(!effect_ID %in% c("P10S4C4", "P10S6C6", "P13S1C1", "P13S1C2", "P23S1C1", "P24S1C2", "P24S1C1", "P25S1C1", "P34S1C1", "P37S1C1", "P37S1C2", "P37S2C5", "P37S2C6", "P37S1C3", "P37S1C4", "P37S2C7", "P37S2C8", "P39S1C1", "P44S1C1"))

prob_use_corr_data_no_spearman_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = prob_use_corr_data_no_spearman)

prob_use_corr_data_no_spearman_model #note, these have not been transformed from z to r yet.

#transform
prob_use_corr_data_no_spearman_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(prob_use_corr_data_no_spearman_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(prob_use_corr_data_no_spearman_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(prob_use_corr_data_no_spearman_model$reg_table$CI.U)),
                                p.val = as.numeric(prob_use_corr_data_no_spearman_model$reg_table$prob)))
prob_use_corr_data_no_spearman_model_results

rm(prob_use_corr_data_no_spearman, prob_use_corr_data_no_spearman_model_results) #remove redundant dataframe
```

## sensitvity analysis for publication status:
```{r}
prob_use_corr_Pub <- prob_use_corr_data %>%  filter(Source_Type == "Published")

prob_use_corr_Pub_model <- robu(formula = yi ~ 1, var.eff.size = vi, studynum = Study_ID, modelweights = "CORR", rho = 0.8, small = TRUE, data = prob_use_corr_Pub)
prob_use_corr_Pub_model

#transform
prob_use_corr_Pub_model_results <- data.frame(cbind(r = as.numeric(psych::fisherz2r(prob_use_corr_Pub_model$reg_table$b.r)),
                                CI.L = as.numeric(psych::fisherz2r(prob_use_corr_Pub_model$reg_table$CI.L)),
                                CI.U = as.numeric(psych::fisherz2r(prob_use_corr_Pub_model$reg_table$CI.U)),
                                p.val = as.numeric(prob_use_corr_Pub_model$reg_table$prob)))
prob_use_corr_Pub_model_results

rm(prob_use_corr_Pub,prob_use_corr_Pub_model_results)
```

Note, for the below there is an insufficient number of unpublished studies to conduct the analysis with robu. Therefore, will use rma.uni.
```{r}
prob_use_corr_UnPub <- prob_use_corr_data %>%  filter(Source_Type == "Unpublished")

prob_use_corr_UnPub_model <- rma.uni(yi=yi, vi = vi,data=prob_use_corr_UnPub,level = 95,digits = 7)
prob_use_corr_UnPub_model

prob_use_corr_UnPub_model_ztor <- predict(prob_use_corr_UnPub_model, digits=7, transf = transf.ztor) 
prob_use_corr_UnPub_model_ztor

rm(prob_use_corr_UnPub)
```

```{r}
macat(es=yi, var=vi, mod=Source_Type, data=prob_use_corr_data, method="random", ztor=TRUE)
```

# Produce Overall Forest plot 
```{r}
produce_prob_use_corr_forest_plot <- function(){
  
  forest(h2_model, 
       atransf=transf.ztor,
       xlim=c(-3.5,3), alim=c(-0.6, 2),
       header="Author(s) and Year",
       slab=prob_use_corr_data$slab, 
       at=transf.rtoz(c(-0.5, 0, .5, .9)),
       order=order(transf.ztor(prob_use_corr_data$yi)), #order by effect size
       xlab="Correlation Coefficient",
       mlab = "",
       addfit = FALSE,
       ilab=as.character(prob_use_corr_data$SR_PROB_Label), ilab.xpos = -1.2) 

addpoly(x = 0.253, ci.lb = 0.202, ci.ub = 0.305, atransf=transf.ztor, row=-0.6, mlab="", cex=1)
abline(h = 0.45)

text(-1.2, 44, "Measure", font=2)
#text(-3.5, -1, pos=4, "RE Model", font=2)
text(-3.5, -0.6, pos=4, "RE Model with RVE (using correlational weighting scheme)", font=2)

segments(transf.rtoz(0.5), -5, transf.rtoz(0.5), 41, lty="dotted") #extra line at r=0.5
  
}
```

Export PDF
```{r}
pdf(file='figures/prob_use_forest.pdf', height=12, width=10)
par(mar=c(4,3.6,0.2,1.5))

produce_prob_use_corr_forest_plot()

par(font=2)
dev.off()
```

Export as png (low res)

```{r}
png(file='figures/prob_use_forest_low_res.png', units = "in", height=13.5, width=10, res=300)
par(mar=c(3.5,3.5,0.2,1.5))

produce_prob_use_corr_forest_plot()

par(font=2)
dev.off()
```

Export as png (high res)

```{r}
png(file='figures/prob_use_forest_high_res.png', units = "in", height=13.5, width=10, res=800)
par(mar=c(3.5,3.5,0.2,1.5))

produce_prob_use_corr_forest_plot()

par(font=2)
dev.off()
```

############## Section 10: combined funnel plot figure ############## 

# Side by side
```{r}
create_side_by_side_funnel <- function(){

layout(matrix(c(1,2,3,4,4,4),ncol=3, byrow=TRUE),
       heights = c(3,0.3),
       width=c(2,2,2))
par(mai = c(1,0.65,1,0.5))


funnel(h1_model, level=c(90, 95, 99), 
               shade=c("gray75", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
               #legend=TRUE,
               back = "white",
               main="A. Media Use",
               cex=1.5, cex.lab=1.5, cex.axis=1.5, cex.main=1.5)   

funnel(h2_model, level=c(90, 95, 99), 
               shade=c("gray75", "#5C6BC0", "#9FA8DA"), 
               atransf = transf.ztor,
              # legend=TRUE,
               back = "white",
               main="B. Problematic Media Use", 
               cex=1.5, cex.lab=1.5, cex.axis=1.5, cex.main=1.5)   

funnel(rq2_model, level=c(90, 95, 99), 
               shade=c("gray75", "#5C6BC0", "#9FA8DA"), 
               atransf = exp,
               xlab = "Ratio of Means",
               back = "white",
               main="C. Reporting Accuracy",
               cex=1.5, cex.lab=1.5, cex.axis=1.5, cex.main=1.5)  

par(mai=c(0,0,0,0))
plot.new()
par(xpd=NA)
legend(x = "top", pch = 1, pt.cex = c(rep(0,4), 2), 
       cex = 2, inset = 0.01, bg = "white", 
       pt.bg <- c("gray75", "#5C6BC0", "#9FA8DA", "white"),
       legend = c("0.10 < p \u2264 1.00", "0.05 < p \u2264 0.10", "0.01 < p \u2264 0.05", "0.00 < p \u2264 0.01"),
       fill = c("gray75", "#5C6BC0", "#9FA8DA", "white"), horiz = TRUE, xpd=NA)

}
```

```{r}
png(file='figures/combined_funnel_side_by_side_low_res.png', units = "in", height=8, width=18, res=300)

create_side_by_side_funnel()

dev.off()
```

```{r}
png(file='figures/combined_funnel_side_by_side_high_res.png', units = "in", height=8, width=18, res=800)

create_side_by_side_funnel()

par(font=2)
dev.off()
```

Export PDF
```{r}
pdf(file='figures/combined_funnel_side_by_side.pdf', height=8, width=18)

create_side_by_side_funnel()

par(font=2)
dev.off()
```

# Clean up environment
```{r}
rm(list = ls())
```







